03-modeling

### 2018-05-16 01_writing/Schratz_hyperspectral.tex
16/05/18

% parameter limits
\begin{table}[b!]
\centering
\caption[t]{10-fold 20-times repeated spatial \ac{CV} performances of lasso, ridge and elasticnet penalties on the plot level and the merged dataset using \ac{RMSE} as the error measure. Values show the overall mean and standard deviation at the repetition level.}
\begingroup\footnotesize
\begin{tabular}{llll}
	\\
	Plot/Penalty   & Lasso         & Ridge        & Elasticnet    \\
	\hline
	Laukiz 1       & 133.15 (4.66) & 86.71 (2.96) & 121.04 (4.15) \\
	Laukiz 2       & 91.93 (6.78)  & 29.73 (0.38) & 47.18 (13.70) \\
	Luiando        & 74.85         & 76.02        & 74.77         \\
	Oiartzun       & 327.93        & 106.65       & 260.38        \\
	Merged dataset & 56.88         & 55.88        & 56.76         \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:penalty_comparison}
\end{table}

@@

When comparing the mean predictive performance of the plot level model against the performance of the super model at the plot level (when the respective plot served as the test set), the supermodel also outperforms the Laukiz 2 model (27.94 vs 30.37 RMSE) (\autoref{tab:supermodel_performance}).

@@

@@

@@

The exact number of contributing pixels of an index cannot be determined as it depends on the location of the tree within the pixel grid.
If a tree is located at the border of a pixel, the same buffer (e.g. 3 m) will include more pixels than if the point is located at the center of a pixel.
Also, if a tree is located at the border of the image data, some directions of the buffer may not contain values.

>>>>

% parameter limits
\begin{table}[b!]
\centering
\caption[t]{10-fold 20-times repeated spatial \ac{CV} performances of lasso, ridge and elasticnet penalties on the plot level and the merged dataset using \ac{RMSE} as the error measure. Values show the overall mean and standard deviation at the repetition level.}
\begingroup\footnotesize
\begin{tabular}{llll}
	\\
	Plot/Penalty   & Lasso         & Ridge         & Elasticnet    \\
	\hline
	Laukiz 1       & 133.15 (4.66) & 86.71 (2.96)  & 121.04 (4.15) \\
	Laukiz 2       & 91.93 (6.78)  & 29.73 (0.38)  & 47.18 (13.70) \\
	Luiando        & 74.83 (0.311) & 75.95 (0.23)  & 74.74 (0.29)  \\
	Oiartzun       & 327.93        & 106.65        & 260.38        \\
	Merged dataset & 54.80 (17.58) & 53.67 (17.95) & 54.66 (17.67) \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:penalty_comparison}
\end{table}

@@

% single models vs supermodel
When comparing the mean predictive performance of the plot level model against the performance of the super model at the plot level (when the respective plot served as the test set), the supermodel also outperforms the Laukiz 2 model (27.94 vs 30.37 RMSE) (\autoref{tab:supermodel_performance}).

@@

% RMSE vs defol and point dens
Laukiz 2 showed contrary results compared to all other plots when linking \ac{RMSE} against mean defoliation and mean point density (\autoref{fig:rmse_defol_dens}).
Laukiz 1, Luiando and Oiartzun show almost identical values in terms of point density (34.35m, 33.77m, 35.01m).
Due to the high similarity, these should be interpreted as a group and not as single values.

@@

\subsubsection{Variable importance}

\ac{NRI}s using bands in the wavelength range of 770 nm - 820 nm (band 80 - band 89), which belongs to the infrared region, appear most often among the ten highest coefficient estimates across all plots (\autoref{tab:variable-importance}).
Only one vegeation index (Datt3) showed up among the most important predictors (Laukiz 1).
Luiando and Oiartzun also prefered bands with longer (938.39 nm (band 114) - 996.31 nm (band 126)) and shorter wavelengths (480.30 nm (band 18) - 503.26 (band 23)).
The first range again belongs to the infrared region while the second is within the region of the visible light, transitioning from blue to green.

@@

The exact number of contributing pixels to the final index value of an observations cannot be determined as it depends on the location of the tree within the pixel grid.
If a tree is located at the border of a pixel, a buffer of e.g. three meters will include more pixels than if the point is located at the center of a pixel.
Also, if a tree is located at the border of the plot, some directions of the buffer will not contain image values.

For Laukiz1, Luiando and Oiartzun \ac{RMSE} seems to increase with a higher point density on a first look.
However, the point densities of these plots are very similar (33.7 m - 35.01 m) and should be interpreted as a group instead of single values.
Comparing this group to Laukiz 2, which has point density of 62 m, the error decreases with a higher point density.
Linking the error against the mean defoliation of a plot does not lead to a clear conclusion:
While Laukiz1, Luiando and Oiartzun give the impression of a decreasing RMSE when defoliation increases, Laukiz 2 clearly shows that a plot with a low defoliation can results in a low RMSE estimate (\autoref{fig:rmse_defol_dens}).

### 2018-05-16 02_scripts/033-luiando/03-modeling_luiando.Rmd
15/05/2018
16/05/18

@@

@@

>>>>

Calculate repetition mean

```{r}
resa_glmnet = readRDS("/data/patrick/mod/hyperspectral/spcv/luiando_ridge_bf2_10folds.rda")
resa_glmnet$measures.test %>% 
  dplyr::mutate(rep = rep(1:20, times = 1, each = 10)) %>% 
  group_by(rep) %>% 
  summarise_at("rmse", mean) %>% 
  summarise(mean(rmse), sd(rmse))
```

@@

Calculate repetition mean

```{r}
resa_glmnet = readRDS("/data/patrick/mod/hyperspectral/spcv/luiando_lasso_bf2_10folds.rda")
resa_glmnet$measures.test %>% 
  dplyr::mutate(rep = rep(1:20, times = 1, each = 10)) %>% 
  group_by(rep) %>% 
  summarise_at("rmse", mean) %>% 
  summarise(mean(rmse), sd(rmse))
```

@@

Calculate repetition mean

```{r}
resa_glmnet = readRDS("/data/patrick/mod/hyperspectral/spcv/luiando_elasticnet.rda")
resa_glmnet$measures.test %>% 
  dplyr::mutate(rep = rep(1:20, times = 1, each = 10)) %>% 
  group_by(rep) %>% 
  summarise_at("rmse", mean) %>% 
  summarise(mean(rmse), sd(rmse))
```

### 2018-05-16 02_scripts/035_all-plots/03-modeling_all.Rmd
16/05/18

@@

>>>>

Calculate repetition mean

```{r}
resa_glmnet = readRDS("/data/patrick/mod/hyperspectral/spcv/all_plots_ridge_bf2_10folds_blocking.rda")
resa_glmnet$measures.test %>% 
  summarise(mean(rmse), sd(rmse))
```

@@

Calculate repetition mean

```{r}
resa_glmnet = readRDS("/data/patrick/mod/hyperspectral/spcv/all_plots_lasso_bf2_10folds_blocking.rda")
resa_glmnet$measures.test %>% 
  summarise(mean(rmse), sd(rmse))
```
